The \dealii{} Library, Version 9.0

### 2018-04-21 9.0/paper.tex
Rewrite the C++11 section.

\dealii{} version 9.0.0 was released April X, 2018. This paper provides an
overview of the new features of this major release and serves as a citable
reference for the \dealii{} software library version 9.0. \dealii{} is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL) from the \dealii{} homepage at
\url{http://www.dealii.org/}.

@@

\item
  \dealii{} first offered support for a subset of C++11 features in
  version 6.2, released in 2009. The current release is the first to \emph{require} a compiler
  supporting C++11. \dealii{} now uses language improvements such as using
  \texttt{emplace\_back()} instead of \texttt{push\_back()}, moving objects
  instead of copying them, using \texttt{nullptr} instead of \texttt{NULL}, and
  marking members with \texttt{=delete;} and \texttt{=default;} where
  appropriate. These changes include some minor incompatibilities: all
  \texttt{clone()} functions (such as \texttt{FiniteElement::clone()} and
  \texttt{Mapping::clone()}) now return \texttt{std::unique\_ptr}s instead of
  C-style raw pointers. Indeed, nearly every interface that returns a pointer
  now returns either a \texttt{std::shared\_ptr} or \texttt{std::unique\_ptr},
  which clarifies object ownership responsibilities and avoids memory leaks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Feature 2}

>>>>

\dealii{} version 9.0.0 was released April X, 2018.
\marginpar{Update the date}
This paper provides an
overview of the new features of this major release and serves as a citable
reference for the \dealii{} software library version 9.0. \dealii{} is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL) from the \dealii{} homepage at
\url{http://www.dealii.org/}.

@@

\item C++11 is now both required and used.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Use of C++11}
\dealii{} first offered support for a subset of C++11 features in
version 6.2, released in 2009. The current release is the first to
\emph{require} a C++11 compiler.

Many parts of the code base have been rewritten to both support and
use the new features of C++11. In particular, \dealii{} now makes
extensive use of move semantics as well as range-based \texttt{for}
loops with \texttt{auto} type deduction of iterator variables. We have
also largely replaced \texttt{push\_back()} by
\texttt{emplace\_back()} when adding elements to collections more
efficiently.

Finally, we have changed the entire code base to avoid using raw
pointers and instead use \texttt{std::unique\_ptr} and
\texttt{std::shared\_ptr} where possible to make memory management
more reliable. These changes include some minor incompatibilities: all
\texttt{clone()} functions (such as \texttt{FiniteElement::clone()} and
\texttt{Mapping::clone()}) now return \texttt{std::unique\_ptr}s instead of
C-style raw pointers. Indeed, nearly all interfaces throughout the library that return a pointer
now return either a \texttt{std::shared\_ptr} or a \texttt{std::unique\_ptr},
thereby clarifying object ownership responsibilities and avoiding memory leaks.
